---
title: "apisensr"
author: "Denis Haine"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_cation: yes
vignette: >
  %\VignetteIndexEntry{apisensr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package `apisensr` provides a graphical interface to the package `episensr`.
To run `apisensr`:

```{r eval=FALSE}
library(apisensr)
run_app()
```

The following functions are available in `episensr` and `apisensr`. Please refer
to `episensr` for more details about these functions.

| Functions available in: | `episensr` | `apisensr app` |
|-------------------------|:----------:|:--------------:|
| selection               | x          | x              |
| mbias                   | x          | x              |
| confounders             | x          | x              |
| confounders.poly        | x          | x              |
| confounders.emm         | x          | x              |
| confounders.limit       | x          | x              |
| confounders.array       | x          | x              |
| confounders.ext         | x          | x              |
| confounders.evalue      | x          |                |
| misclassification       | x          | x              |
| misclassification_cov   | x          | x              |
| bootstrap               | x          |                |
| multidimBias            | x          | x              |
| probsens.sel            | x          | x              |
| probsens.conf           | x          | x              |
| probsens                | x          | x              |
| probsens.irr.conf       | x          |                |
| probsens.irr            | x          |                |
| multiple bias           | x          |                |
